How single mutations affect viral escape from broad and narrow antibodies to H1 influenza hemagglutinin

### 2018-02-23 paper/CoverLetter_FinalNatureCommunications.tex
near complete final version to submit, just need to add signature to Licence To Publish Form
slight revisions requested by editorial staff at _Nature Communications_

@@

\item We have provided publication-quality versions of all figures as separate files, and moved the legends to the end of the manuscript. {\color{red}STILL NEEDS TO BE DONE.}

@@

\item We have provided the Supplementary Information as a separate PDF, which the \textit{Nature Communications} author instructions indicate is an acceptable substitute for a Word document. The reason that we are providing it is a PDF rather than a Word document is that it is written in LaTex. {\color{red} Still need to be done.}

>>>>

Regarding the question of whether we want transparent peer review, the substantive reviewer comments were made in the initial round of reviews for \textit{Nature Microbiology} that were then transferred to \textit{Nature Communications}.
If those reviewer comments can be used, then yes we would like to opt for publication of the reviewer comments.
However, our understanding is that perhaps this option can only be used for the reviews for the second round with \textit{Nature Communications.}
If that is the case, then we opt \emph{not} to include the reviewer comments, since these comments for this second round of review are cursory and not particularly informative in the absence of the initial reviews for \textit{Nature Microbiology}.

@@

\item We have provided publication-quality versions of all figures as separate files, and moved the legends to the end of the manuscript.

@@

\item We have provided the Supplementary Information as a separate PDF, which the \textit{Nature Communications} author instructions indicate is an acceptable substitute for a Word document. The reason that we are providing it is a PDF rather than a Word document is that it is written in LaTex.

### 2018-02-23 paper/FinalNatureCommunicationsSubmissionFiles/manuscript_figsatend_nosupp.tex
slight revisions requested by editorial staff at _Nature Communications_

\subsection*{The effects of all mutations on antibody neutralization}
We performed mutational antigenic profiling using the three broad antibodies at the concentrations indicated in Figure~\ref{fig:neutcurves}. 
All experiments were performed in full biological triplicate using three independently generated virus libraries carrying single amino-acid mutations to HA\cite{doud2016accurate}.
Importantly, as described previously\cite{doud2016accurate}, these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.

@@

\subsection*{COMPETING INTERESTS}
The authors declare no competing financial interests.

>>>>

\subsection*{The effects of all mutations on antibody neutralization}
We performed mutational antigenic profiling using the three broad antibodies at the concentrations indicated in Figure~\ref{fig:neutcurves} (the fraction of each library neutralized at each of these concentrations is listed in Supplementary Table~1). 
All experiments were performed in full biological triplicate using three independently generated virus libraries carrying single amino-acid mutations to HA\cite{doud2016accurate}.
Importantly, as described previously\cite{doud2016accurate}, these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.

@@

\subsection*{COMPETING INTERESTS}
The authors declare no competing interests, financial or otherwise.

### 2018-02-23 paper/manuscript.tex
slight revisions requested by editorial staff at _Nature Communications_

\subsection*{The effects of all mutations on antibody neutralization}
We performed mutational antigenic profiling using the three broad antibodies at the concentrations indicated in Figure~\ref{fig:neutcurves}. 
All experiments were performed in full biological triplicate using three independently generated virus libraries carrying single amino-acid mutations to HA\cite{doud2016accurate}.
Importantly, as described previously\cite{doud2016accurate}, these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.

>>>>

\subsection*{The effects of all mutations on antibody neutralization}
We performed mutational antigenic profiling using the three broad antibodies at the concentrations indicated in Figure~\ref{fig:neutcurves} (the fraction of each library neutralized at each of these concentrations is listed in Supplementary Table~\ref{supptab:fracsurvive}). 
All experiments were performed in full biological triplicate using three independently generated virus libraries carrying single amino-acid mutations to HA\cite{doud2016accurate}.
Importantly, as described previously\cite{doud2016accurate}, these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.
